DynaProg for Scala

### 2013-01-10 docs/report/introduction.tex
Nits in build.sbt.

\subsubsection{Lightweight Modular Staging}
Lightweight Modular Staging (LMS) \cite{lms}, \cite{lms_thesis} is a runtime code generation built on top of Scala virtualized \cite{scala_virtualized} that uses types to distinguish between binding time (compilation and runtime) for code compilation. This framework can be extended to generate from the same source code efficient implementation for heterogeneous platforms at runtime \cite{lms2}, \cite{lms3}, \cite{delite}.

>>>>

\subsubsection{Lightweight Modular Staging}
Lightweight Modular Staging (LMS) \cite{lms}, \cite{lms_thesis} is a runtime code generation built on top of Scala virtualized \cite{scala_virtualized} that uses types to distinguish between binding time (compilation and runtime) for code compilation. This framework has been extended to generate from the same source code efficient implementation for heterogeneous platforms at runtime (Delite) \cite{lms2}, \cite{lms3}, \cite{delite}.
